---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mBAT

<!-- badges: start -->
<!-- badges: end -->

Multivariate set-Based Association Test (mBAT), a novel gene-based method, to improve power of identifying genes harbouring variants with masking effects.
We show by extensive simulations that mBAT has greater power than the sum-χ^2 strategy (taking fastBAT and MAGMA as examples) in the presence of masking effects. 
To maximise overall power regardless of the masking effects, we further proposed a hybrid method, mBAT-combo, by combining mBAT and fastBAT test statistics through a Cauchy combination method, a recently developed method to combine different test statistics without knowing the correlation structure(Liu Y, Chen S, Li Z, Morrison AC, Boerwinkle E, Lin X. ACAT: A Fast and Powerful p Value Combination Method for Rare-Variant Analysis in Sequencing Studies. Am J Hum Genet. 2019 Mar 7;104(3):410-421. doi: 10.1016/j.ajhg.2019.01.002. PMID: 30849328; PMCID: PMC6407498.).

## Installation

You can install the development version of mBAT from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Share-AL-work/mBAT.combo")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(mBAT)
```

## 1. set path
```{r extract file}
path <- system.file("extdata",package = "mBAT")
list.files(path)

bim_file <- paste0(path,"/","Chr19_ABHD17A.txt")
gene_sum_file <- paste0(path,"/","Chr19_ABHD17A.txt")
LD_file_prefix <- paste0(path,"/","Chr19_ABHD17A.txt.ldm.full")
fastBAT_file <- paste0(path,"/","noDT_Vitamin_D_Chr19.gene.fastbat")
```

## 2. Do analysis
``` {r analysis}
bim_file="/Users/uqali4/mBAT_development_R/mBAT.combo/inst/extdata/1000G_eur_unrel_ukbcom22.bim"
map_file="/Users/uqali4/mBAT_development_R/mBAT.combo/inst/extdata/hg19_v40_glist_Pat_v1.txt"
assoc_file="/Users/uqali4/mBAT_development_R/mBAT.combo/inst/extdata/Chr22.fastGWA.ma"
LD_path="/Users/uqali4/mBAT_development_R/mBAT.combo/inst/extdata/LD_Chr22"
result_path="/Users/uqali4/mBAT_development_R/mBAT.combo/inst/extdata"
fastBAT_output="/Users/uqali4/mBAT_development_R/mBAT.combo/inst/extdata/fb_Chr22_1kg.gene.fastbat"
prop=0.9
#res <- mBAT_combo(bim_file,
#                  map_file,
#                  assoc_file,
#                  LD_path,
#                  result_path,
#                  fastBAT_output,
#                  prop,
#                  gene_annotate)
#head(res)
```


#n that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
